Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Work on study design

Secondly, probably the topic of most interest to our research is \emph{issue quality}.
This field is mainly concerned with software tickets and their characteristics: how
important

>>>>

Secondly, probably the topic of most interest to our research is \emph{issue quality}.
This field is mainly concerned with software tickets and their characteristics: how
important are issue trackers to a software project, what makes for a good bug report,
what impact does bad triaging have etc. While reading multipe
